Team size and composition in home health care

### 2023-10-25 paper-presentation/paper-presentation.qmd
Final version

---
title: "Team size and composition in home health care"
author: "René Bekker, Yoram Clapper, Witek ten Hove and Dennis Moeke"
format:
  revealjs:
    navigation-mode: vertical
    theme: [default, custom.scss]
bibliography: references.bib
execute:
  output: true
jupyter: python3
---

# Decision problem

@@

@@

where [$\rho$]{style="color: red;"} $= m_am_sm_g$ is the average demand, and [$z$]{style="color: red;"} is the peakedness given by $$z = \frac{\sigma_g^2}{m_g} + m_g + m_g(1−G_s)(\frac{\sigma_a^2}{m_a}-1)$$.

@@

::: columns
::: {.column width="40%"}
Hence, the utilization of the capacity [$C$]{style="color: red;"} is $$\frac{\mathbb{E}[N]}{C} = \frac{1}{1 + \frac{\gamma\sqrt{z}}{\sqrt{\rho}}} $$
:::

@@

*The buffer capacity required to handle demand variability decreases with scale, but the possible reduction becomes smaller as the scale increases.*

@@

Let M be the total number of scheduled care workers during some period [$T$]{style="color: red;"}, and let [$p$]{style="color: red;"} be the probability that the care worker is present.

@@

::: columns
::: {.column width="75%"}
```{python}
#------------------------------------------------------------------------------
# Principle 4: team composition
#------------------------------------------------------------------------------

@@

# generates image of optimal capacity distribution over qualification level
# maxQ (int): highest qualification level (ranked by integer values)
# mu (list): mean weekly demand per qualification level
# sigma (list): standard deviation of weekly demand per qualification level
# z (float): service level (based on normal distribution)
# max_rate: upper limit x-axis (scaling by arrival rate)
# min_rate: lower limit x-axis (scaling by arrival rate)
def plot_optimal_cap_on_qlevel(maxQ,mu,sigma,z,min_rate,max_rate):
    fig, ax = plt.subplots(figsize=(9.6,7.2))
    mu = np.array(mu)
    sigma = np.array(sigma)

@@

    limx = ax.get_ylim()
    ax.vlines(1, ymin=limx[0], ymax=limx[1], color='grey', linestyles='dashed')
    # ax.vlines(2, ymin=limx[0], ymax=limx[1], color='grey', linestyles='dashed')

@@

@@

## Principle 6

>>>>

---
title: "Team size and composition in home health care"
author: "René Bekker, Yoram Clapper, Witek ten Hove and Dennis Moeke"
format:
  revealjs:
    logo: images/logo-h.png
    navigation-mode: vertical
    theme: [default, custom.scss]
bibliography: references.bib
execute:
  output: true
jupyter: python3
---

# Social issue

![@ministerie_van_volksgezondheid_home_2020](images/supply.png)

## Social issue

```{python}
import pandas as pd
import plotly.graph_objects as go

# Read the CSV file
df = pd.read_csv('absenteeism.csv')
df

# Create the line chart
fig = go.Figure()

# Add the trace for the data
fig.add_trace(go.Scatter(x=df['periode'], y=df['verzuim'], mode='lines', line_color='tomato', name='Absenteeism Percentages'))

# Title and labels (translated to English)
fig.update_layout(
    title='Absenteeism Percentages Dutch Healthcare Sector<br><sub>Annual Figures (%)</sub>',
    xaxis_title='Period',
    yaxis_title='Percentage',
    annotations=[
        dict(
            x=1,
            y=-0.2,
            xref='paper',
            yref='paper',
            text='Source: CBS',
            showarrow=False
        )
    ]
)

# Display the chart
fig.show()
```

## Decision problem

@@

## Business problem

-   What are demand dynamics?
-   What are appropriate team sizes?

@@

where [$\rho$]{style="color: red;"} $= m_am_sm_g$ is the average demand, and [$z$]{style="color: red;"} is the peakedness given by $$z = \frac{\sigma_g^2}{m_g} + m_g + m_g(1−G_s)(\frac{\sigma_a^2}{m_a}-1)$$
Hence, the utilization of the capacity [$C$]{style="color: red;"} is $$\frac{\mathbb{E}[N]}{C} = \frac{1}{1 + \frac{\gamma\sqrt{z}}{\sqrt{\rho}}}$$

@@

::: columns
::: {.column width="40%"}
*The buffer capacity required to handle demand variability decreases with scale, but the possible reduction becomes smaller as the scale increases.*

[NB: The available data is limited to planned care and may not accurately reflect the actual demand for home care.]{style="color: red;"}
:::

@@

@@

Let [$M$]{style="color: red;"} be the total number of scheduled care workers during some period [$T$]{style="color: red;"}, and let [$p$]{style="color: red;"} be the probability that the care worker is present.

@@

::: columns
::: {.column width="75%"}

```{python}
#------------------------------------------------------------------------------
# Principle 4: team composition
#------------------------------------------------------------------------------

@@

# generates image of optimal capacity distribution over qualification level
# maxQ (int): highest qualification level (ranked by integer values)
# mu (list): mean weekly demand per qualification level
# sigma (list): standard deviation of weekly demand per qualification level
# z (float): service level (based on normal distribution)
# max_rate: upper limit x-axis (scaling by arrival rate)
# min_rate: lower limit x-axis (scaling by arrival rate)
def plot_optimal_cap_on_qlevel(maxQ,mu,sigma,z,min_rate,max_rate):
    fig, ax = plt.subplots(figsize=(14,6.8))
    mu = np.array(mu)
    sigma = np.array(sigma)

@@

    limx = ax.get_ylim()
    ax.vlines(1, ymin=limx[0], ymax=limx[1], color='grey', linestyles='dashed')
    fig.text(.5, .01, 'Ratio in capacity $C_k/ ∑_{j∈Q} C_j$ as mean number of new clients $m_a$ increases; dashed horizontal lines represent ratios in demand $μ_k/ ∑_{j∈Q} μ_j$. Dashed vertical line corresponds to current demand.', ha='center')
    plt.show()  # This will display the plot
    plt.close()

@@

*Small teams must deploy above-average amounts of high-level care workers to sufficiently cope with the variability in demand. As the scale increases, the amount of capacity required will move closer to the average workload for each qualification level.*

@@
